Age-related changes in plant growth and traits

### 2015-08-26 Accessory_figs.rmd
starting to get scripts to run again - accessory_figs runs with a few small hitches (i.e. not using SE)

@@

mod <- lm(log(seed_size)~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
plot(asin(sqrt(prop_accessory))~seed_size,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=.9)
words.bottom.right.logx(mod)
points(asin(sqrt(prop_accessory))~seed_size,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
mtext("seed size (mg)",1, outer=TRUE,cex=1.2)

@@

mod <- lm(log(total_weight)~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
plot(asin(sqrt(prop_accessory))~total_weight,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=0.9)
points(asin(sqrt(prop_accessory))~total_weight,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
words.bottom.right.logx(mod)
mtext("total plant weight (mg)",1, outer=TRUE,cex=1.2)

mod <- lm(log(seedset)~log(accessory_per_seed),SummarySpp[["mean"]])
plot((accessory_per_seed)~seedset,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="accessory costs per successful seed",xlab="",cex=0.9)
points((accessory_per_seed)~seedset,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
words.top.right.logxy(mod)

mod <- lm(log(seedset)~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
plot(asin(sqrt(prop_accessory))~seedset,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=0.9)
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
points(asin(sqrt(prop_accessory))~seedset,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
words.top.right.logx(mod)
mtext("seedset",1, outer=TRUE,cex=1.2)

par(mfrow=c(1,2), cex=1, omi=c(0.4,0.6,0.7,0.3), mai=c(1.1,1,0.3,0.3))
mod <- lm(log(prepollen_all_per_seed)~log(accessory_per_seed),SummarySpp[["mean"]])
plot((accessory_per_seed)~(prepollen_all_per_seed),SummaryInd, log="xy",pch=16,col=col.spp(species),ylab="accessory costs per successful seed",cex=0.9)
points((accessory_per_seed)~prepollen_all_per_seed,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
words.bottom.right.logxy(mod)

mod <- lm(asin(sqrt(prop_prepollen_all))~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
plot(asin(sqrt(prop_accessory))~asin(sqrt(prop_prepollen_all)),SummaryInd, log="", pch=16,col=col.spp(species),ylab="proportional accessory costs",cex=0.9)
points(asin(sqrt(prop_accessory))~asin(sqrt(prop_prepollen_all)),SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
words.bottom.right(mod)
```

@@

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14,warning=FALSE}
par(mfrow=c(2,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
mod <- lm(asin(sqrt(seedset))~asin(sqrt(RA)),data=subset(SummaryInd,seedset>0&seedset<1))
plot(asin(sqrt(RA))~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
words.bottom.right(mod)

mod <- lm(asin(sqrt(prop_propagule))~asin(sqrt(RA)),data=subset(SummaryInd,prop_propagule>0))
plot(asin(sqrt(RA))~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
words.bottom.right(mod)
legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

mod <- lm(asin(sqrt(propagule_per_seed))~asin(sqrt(RA)),data=subset(SummaryInd,prop_propagule>0))
plot(asin(sqrt(RA))~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="x",pch=16,col=col.spp(species))
words.bottom.right.logx(mod)
```

@@

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14,warning=FALSE}
par(mfrow=c(2,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
options(scipen=20)
mod <- lm(asin(sqrt(seedset))~log(repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
plot((repro_inv)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="y")
words.bottom.right.logy(mod)

mod <- lm(asin(sqrt(prop_propagule))~log(repro_inv),data=subset(SummaryInd,prop_propagule>0))
plot((repro_inv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="y")
words.bottom.right.logy(mod)
legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

mod <- lm(log(propagule_per_seed)~log(repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
plot((repro_inv)~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="xy",pch=16,col=col.spp(species))
words.bottom.right.logxy(mod)
```

@@

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14,warning=FALSE}
par(mfrow=c(2,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
options(scipen=20)
mod <- lm((prop_maxH)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1))
plot(asin(sqrt(seedset))~(prop_maxH),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
words.bottom.right(mod)

mod <- lm(log(height)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1))
plot(asin(sqrt(seedset))~(height),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="x")
words.bottom.right.logx(mod)

mod <- lm((prop_maxH)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,prop_propagule>0))
plot(asin(sqrt(prop_propagule))~(prop_maxH),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
words.bottom.right(mod)
legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

mod <- lm((prop_maxH)~log(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1))
plot((propagule_per_seed)~(prop_maxH),data=subset(SummaryInd,seedset>0&seedset<1), log="y",pch=16,col=col.spp(species))
words.bottom.right.logy(mod)
```

@@

mod <- lm(log(RA)~log((propagule_inv)),data=subset(SummaryInd,RA>0&propagule_inv>0))
plot(propagule_inv~RA,data=subset(SummaryInd,RA>0&propagule_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to propagules (mg)")
words.bottom.right.logxy(mod)

mod <- lm(log(RA)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,RA>0&prop_propagule>0))
plot(asin(sqrt(prop_propagule))~RA,data=subset(SummaryInd,RA>0&prop_propagule>0), log="x", pch=16,col=col.spp(species),ylab="propagules (as proportion repro inv)")
words.bottom.left.logx(mod)

mod <- lm(log(RA)~log((prepollen_aborted_inv)),data=subset(SummaryInd,RA>0&prepollen_aborted_inv>0))
plot(prepollen_aborted_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp(species),log="xy",ylab="pre-pollination aborted tissues (mg)")
words.bottom.right.logxy(mod)

mod <- lm(log(RA)~asin(sqrt(prop_prepollen_aborted)),data=subset(SummaryInd,RA>0&prop_prepollen_aborted>0))
plot(asin(sqrt(prop_prepollen_aborted))~RA,data=subset(SummaryInd,RA>0&prop_prepollen_aborted>0), pch=16,col=col.spp(species), log="x",ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
words.bottom.right.logx(mod)

mod <- lm(log(RA)~log((prepollen_success_inv)),data=subset(SummaryInd,RA>0&prepollen_success_inv>0))
plot(prepollen_success_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp(species),log="xy",ylab="pre-pollination successful tissues (mg)")
words.bottom.right.logxy(mod)

mod <- lm(log(RA)~asin(sqrt(prop_prepollen_success)),data=subset(SummaryInd,RA>0&prop_prepollen_success>0))
plot(asin(sqrt(prop_prepollen_success))~RA,data=subset(SummaryInd,RA>0&prop_prepollen_success>0), pch=16,col=col.spp(species), log="x",ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
words.bottom.right.logx(mod)

mod <- lm(log(RA)~log((packaging_dispersal_inv)),data=subset(SummaryInd,RA>0&packaging_dispersal_inv>0))
plot(packaging_dispersal_inv~RA,data=subset(SummaryInd,RA>0&packaging_dispersal_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to packaging and dispersal (mg)")
words.bottom.right.logxy(mod)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

mod <- lm(log(RA)~asin(sqrt(prop_packaging_dispersal)),data=subset(SummaryInd,RA>0&prop_packaging_dispersal>0))
plot(asin(sqrt(prop_packaging_dispersal))~RA,data=subset(SummaryInd,RA>0&prop_packaging_dispersal>0), log="x", pch=16,col=col.spp(species),ylab="packaging and dispersal (as proportion repro inv)")
words.bottom.left.logx(mod)

mod <- lm(log(RA)~log((postpollen_aborted_inv)),data=subset(SummaryInd,RA>0&postpollen_aborted_inv>0))
plot(postpollen_aborted_inv~RA,data=subset(SummaryInd,RA>0&postpollen_aborted_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to tissues aborted postpollination (mg)")
words.bottom.right.logxy(mod)

mod <- lm(log(RA)~asin(sqrt(prop_postpollen_aborted)),data=subset(SummaryInd,RA>0&prop_postpollen_aborted>0))
plot(asin(sqrt(prop_postpollen_aborted))~RA,data=subset(SummaryInd,RA>0&prop_postpollen_aborted>0), log="x", pch=16,col=col.spp(species),ylab="tissues aborted postpollination (as proportion repro inv)")
words.bottom.left.logx(mod)
```

##6. Shifts in proportion to tissue types across species  
- Reasonably idiosyncratic patterns  
- Species very different in which accessory tissues they invest the most in - which reflects the differences in basic structure (i.e. Banksia cones), but also more subtlely that some species abort lots of buds (pre-pollination aborted), while other species abort more fully formed flowers   
- COER, EPMI, LEES, PILI invest the most energy in propagules  
- HATE invests by far the least into propagules  
```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=28,warning=FALSE}
par(mfrow=c(4,2), cex=1, omi=c(1,.1,.7,.1), mai=c(.5,1.1,.2,0.2))  
mean1 <- SummarySpp$prop_propagule
se1 <- SummarySpp$prop_propagule_se
plot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.002,.25),ylab="propagules",xlab="")
se_function(mean1,se1)

mean1 <- SummarySpp$propagule_per_seed
se1 <- SummarySpp$propagule_per_seed_se
plot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylab="propagules",xlab="")
se_function(mean1,se1)

mean1 <- SummarySpp$prop_prepollen_all
se1 <- SummarySpp$prop_prepollen_all_se
plot(mean1~species,data=subset(SummarySpp[["mean"]]),cex.axis=.5,pch=16,ylim=c(.1,1),ylab="pre-pollination tissues",xlab="")
se_function(mean1,se1)

mean1 <- SummarySpp$prepollen_all_per_seed
se1 <- SummarySpp$prepollen_all_per_seed_se
plot((.01+prepollen_all_per_seed)~species,data=subset(SummarySpp[["mean"]]),cex.axis=.5,pch=16,ylab="pre-pollination tissues",xlab="",log="y")
se_function(mean1,se1)

mean1 <- SummarySpp$prop_packaging_dispersal
se1 <- SummarySpp$prop_packaging_dispersal_se
plot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="packaging and dispersal")
se_function(mean1,se1)

mean1 <- SummarySpp$packaging_dispersal_per_seed
se1 <- SummarySpp$packaging_dispersal_per_seed_se
plot((packaging_dispersal_per_seed+.1)~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,ylab="packaging and dispersal",log="y")
se_function(mean1,se1)

mean1 <- SummarySpp$prop_postpollen_aborted
se1 <- SummarySpp$prop_postpollen_aborted_se
plot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="aborted post-pollination tissues")
se_function(mean1,se1)

mean1 <- SummarySpp$postpollen_aborted_per_seed
se1 <- SummarySpp$postpollen_aborted_per_seed_se
plot((postpollen_aborted_per_seed+.1)~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,ylab="aborted post-pollination tissues",log="y")
se_function(mean1,se1)

@@

plot(mean~species,
     tmp,
     cex.axis=.5,pch=16,log="y",ylim=c(.02,1),
     ylab="Prop reproductive investment put into pre-pollination tissues")

@@

plot(mean~species,
     tmp2,
     cex.axis=.5,pch=16,log="y",ylim=c(0.08,.8),
     ylab="Prop reproductive investment put into packaging & dispersal tissues")

>>>>

```{r}
remake::make("export")

SummaryInd <- readRDS("export/SummaryInd.rds")
SummarySpp <- readRDS("export/SummarySpp.rds")
SummarySppAge <- readRDS("export/SummarySppAge.rds")

source("R/figures.R")
```

@@

mod <- lm(log(seed_size)~prop_accessory,SummarySpp[["mean"]])
plot(prop_accessory~seed_size,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=.9)
words.bottom.right.logx(mod)
points(prop_accessory~seed_size,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
mtext("seed size (mg)",1, outer=TRUE,cex=1.2)

@@

mod <- lm(log(total_weight)~prop_accessory,SummarySpp[["mean"]])
plot(prop_accessory~total_weight,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=0.9)
points(prop_accessory~total_weight,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
words.bottom.right.logx(mod)
mtext("total plant weight (mg)",1, outer=TRUE,cex=1.2)

mod <- lm(log(seedset)~log(accessory_per_seed),SummarySpp[["mean"]])
plot(accessory_per_seed~seedset,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="accessory costs per successful seed",xlab="",cex=0.9)
points(accessory_per_seed~seedset,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
words.top.right.logxy(mod)

mod <- lm(log(seedset)~prop_accessory,SummarySpp[["mean"]])
plot(prop_accessory~seedset,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=0.9)
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
points(prop_accessory~seedset,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
words.top.right.logx(mod)
mtext("seedset",1, outer=TRUE,cex=1.2)

par(mfrow=c(1,2), cex=1, omi=c(0.4,0.6,0.7,0.3), mai=c(1.1,1,0.3,0.3))
mod <- lm(log(prepollen_all_per_seed)~log(accessory_per_seed),SummarySpp[["mean"]])
plot(accessory_per_seed~(prepollen_all_per_seed),SummaryInd, log="xy",pch=16,col=col.spp(species),ylab="accessory costs per successful seed",cex=0.9)
points(accessory_per_seed~prepollen_all_per_seed,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
words.bottom.right.logxy(mod)

mod <- lm(prop_prepollen_all~prop_accessory,SummarySpp[["mean"]])
plot(prop_accessory~prop_prepollen_all,SummaryInd, log="", pch=16,col=col.spp(species),ylab="proportional accessory costs",cex=0.9)
points(prop_accessory~prop_prepollen_all,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
words.bottom.right(mod)
```

SummarySpp[["mean"]]$accessory_per_seed

@@

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14,warning=FALSE}
par(mfrow=c(2,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
mod <- lm(seedset~RA,data=subset(SummaryInd,seedset>0&seedset<1))
plot(RA~seedset,data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
words.bottom.right(mod)

mod <- lm(prop_propagule~RA,data=subset(SummaryInd,prop_propagule>0))
plot(RA~prop_propagule,data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
words.bottom.right(mod)
legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

mod <- lm(propagule_per_seed~RA,data=subset(SummaryInd,seedset>0&seedset<1))
plot(RA~propagule_per_seed,data=subset(SummaryInd,seedset>0&seedset<1), log="x",pch=16,col=col.spp(species))
words.bottom.right.logx(mod)
```

@@

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14,warning=FALSE}
par(mfrow=c(2,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
options(scipen=20)
mod <- lm(seedset~log(repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
plot(repro_inv~seedset,data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="y")
words.bottom.right.logy(mod)

mod <- lm(prop_propagule~log(repro_inv),data=subset(SummaryInd,prop_propagule>0))
plot(repro_inv~prop_propagule,data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="y")
words.bottom.right.logy(mod)
legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

mod <- lm(log(propagule_per_seed)~log(repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
plot(repro_inv~propagule_per_seed,data=subset(SummaryInd,seedset>0&seedset<1), log="xy",pch=16,col=col.spp(species))
words.bottom.right.logxy(mod)
```

@@

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14,warning=FALSE}
par(mfrow=c(2,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
options(scipen=20)
mod <- lm(prop_maxH~seedset,data=subset(SummaryInd,seedset>0&seedset<1))
plot(seedset~prop_maxH,data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
words.bottom.right(mod)

mod <- lm(log(height)~seedset,data=subset(SummaryInd,seedset>0&seedset<1))
plot(seedset~height,data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="x")
words.bottom.right.logx(mod)

mod <- lm(prop_maxH~prop_propagule,data=subset(SummaryInd,prop_propagule>0))
plot(prop_propagule~prop_maxH,data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
words.bottom.right(mod)
legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

mod <- lm(prop_maxH~log(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1))
plot(propagule_per_seed~prop_maxH,data=subset(SummaryInd,seedset>0&seedset<1), log="y",pch=16,col=col.spp(species))
words.bottom.right.logy(mod)
```

@@

mod <- lm(RA~log(propagule_inv),data=subset(SummaryInd,RA>0&propagule_inv>0))
plot(propagule_inv~RA,data=subset(SummaryInd,RA>0&propagule_inv>0), pch=16,col=col.spp(species),log="y", ylab="energy to propagules (mg)")
words.top.left.logxy(mod)

mod <- lm(RA~prop_propagule,data=subset(SummaryInd,RA>0&prop_propagule>0))
plot(prop_propagule~RA,data=subset(SummaryInd,RA>0&prop_propagule>0), log="", pch=16,col=col.spp(species),ylab="propagules (as proportion repro inv)")
words.bottom.left.logx(mod)

mod <- lm(RA~log(prepollen_aborted_inv),data=subset(SummaryInd,RA>0&prepollen_aborted_inv>0))
plot(prepollen_aborted_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp(species),log="y",ylab="pre-pollination aborted tissues (mg)")
words.top.left.logxy(mod)

mod <- lm(RA~prop_prepollen_aborted,data=subset(SummaryInd,RA>0&prop_prepollen_aborted>0))
plot(prop_prepollen_aborted~RA,data=subset(SummaryInd,RA>0&prop_prepollen_aborted>0), pch=16,col=col.spp(species), log="",ylab="pre-pollination aborted tissues (as proportion repro inv)")
words.bottom.right.logx(mod)

mod <- lm(RA~log(prepollen_success_inv),data=subset(SummaryInd,RA>0&prepollen_success_inv>0))
plot(prepollen_success_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp(species),log="y",ylab="pre-pollination successful tissues (mg)")
words.top.left.logxy(mod)

mod <- lm(RA~prop_prepollen_success,data=subset(SummaryInd,RA>0&prop_prepollen_success>0))
plot(prop_prepollen_success~RA,data=subset(SummaryInd,RA>0&prop_prepollen_success>0), pch=16,col=col.spp(species), log="",ylab="pre-pollination successful tissues (as proportion repro inv)")
words.bottom.right.logx(mod)

mod <- lm(RA~log(packaging_dispersal_inv),data=subset(SummaryInd,RA>0&packaging_dispersal_inv>0))
plot(packaging_dispersal_inv~RA,data=subset(SummaryInd,RA>0&packaging_dispersal_inv>0), pch=16,col=col.spp(species),log="y", ylab="energy to packaging and dispersal (mg)")
words.bottom.right.logxy(mod)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

mod <- lm(RA~prop_packaging_dispersal,data=subset(SummaryInd,RA>0&prop_packaging_dispersal>0))
plot(prop_packaging_dispersal~RA,data=subset(SummaryInd,RA>0&prop_packaging_dispersal>0), log="", pch=16,col=col.spp(species),ylab="packaging and dispersal (as proportion repro inv)")
words.bottom.left.logx(mod)

mod <- lm(RA~log(postpollen_aborted_inv),data=subset(SummaryInd,RA>0&postpollen_aborted_inv>0))
plot(postpollen_aborted_inv~RA,data=subset(SummaryInd,RA>0&postpollen_aborted_inv>0), pch=16,col=col.spp(species),log="y", ylab="energy to tissues aborted postpollination (mg)")
words.bottom.right.logxy(mod)

mod <- lm(RA~prop_postpollen_aborted,data=subset(SummaryInd,RA>0&prop_postpollen_aborted>0))
plot(prop_postpollen_aborted~RA,data=subset(SummaryInd,RA>0&prop_postpollen_aborted>0), log="", pch=16,col=col.spp(species),ylab="tissues aborted postpollination (as proportion repro inv)")
words.bottom.left.logx(mod)
```

##6. Shifts in proportion to tissue types across species  
- Reasonably idiosyncratic patterns  
- Species very different in which accessory tissues they invest the most in - which reflects the differences in basic structure (i.e. Banksia cones), but also more subtlely that some species abort lots of buds (pre-pollination aborted), while other species abort more fully formed flowers   
- COER, EPMI, LEES, PILI invest the most energy in propagules  
- HATE invests by far the least into propagules  
```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=28,warning=FALSE}
par(mfrow=c(4,2), cex=1, omi=c(1,.1,.7,.1), mai=c(.5,1.1,.2,0.2))  
mean1 <- SummarySpp[["mean"]]$prop_propagule
se1 <- SummarySpp[["sd"]]$prop_propagule
boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylab="proportion propagules",xlab="")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$propagule_per_seed
se1 <- SummarySpp[["sd"]]$propagule_per_seed
boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylab="propagules",xlab="")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$prop_prepollen_all
se1 <- SummarySpp[["sd"]]$prop_prepollen_all
boxplot(mean1~species,data=subset(SummarySpp[["mean"]]),cex.axis=.5,pch=16,ylim=c(.1,1),ylab="pre-pollination tissues",xlab="")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$prepollen_all_per_seed
se1 <- SummarySpp[["sd"]]$prepollen_all_per_seed
boxplot((.01+prepollen_all_per_seed)~species,data=subset(SummarySpp[["mean"]]),cex.axis=.5,pch=16,ylab="pre-pollination tissues",xlab="",log="y")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$prop_packaging_dispersal
se1 <- SummarySpp[["sd"]]$prop_packaging_dispersal
boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="packaging and dispersal")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$packaging_dispersal_per_seed
se1 <- SummarySpp[["sd"]]$packaging_dispersal_per_seed
boxplot((packaging_dispersal_per_seed+.1)~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,ylab="packaging and dispersal",log="y")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$prop_postpollen_aborted
se1 <- SummarySpp[["sd"]]$prop_postpollen_aborted
boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="aborted post-pollination tissues")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$postpollen_aborted_per_seed
se1 <- SummarySpp[["sd"]]$postpollen_aborted_per_seed
boxplot((postpollen_aborted_per_seed+.1)~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,ylab="aborted post-pollination tissues",log="y")
se_function(mean1,se1)

@@

plot(mean~as.factor(species),
     tmp,
     cex.axis=.5,pch=16,log="y",ylim=c(.02,1),
     ylab="Prop reproductive investment put into pre-pollination tissues")

@@

plot(mean~as.factor(species),
     tmp2,
     cex.axis=.5,pch=16,log="y",ylim=c(0.08,.8),
     ylab="Prop reproductive investment put into packaging & dispersal tissues")

### 2015-08-26 RA_figs.rmd
starting to get scripts to run again - accessory_figs runs with a few small hitches (i.e. not using SE)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="",xlab="",ylab="",cex=1.4, xlim=c(0,1), ylim=c(0,1),
                    main=spp,col=col.age(data[[spp]]$age))
}

>>>>

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="",xlab="",ylab="",cex=1, xlim=c(0,1), 
                    main=spp,col=col.age(data[[spp]]$age))
}
